### 2021-08-13 paper/paper.tex
phrase not too uncommon sounds awkward

Since functions are first-class citizens in Julia, they can be passed around
and used efficiently. Thus, everything that acts like a function can be used
in \trixi, \eg, to define initial/boundary conditions. While the flexibility
to change initial/boundary conditions
is not too uncommon, two-point numerical fluxes are also just functions with a
specified signature. Thus, users can implement numerical fluxes in their
own code and they will work and be as efficient as if they were implemented
directly in \trixi.

>>>>

Since functions are first-class citizens in Julia, they can be passed around
and used efficiently. Thus, everything that acts like a function can be used
in \trixi, \eg, to define initial/boundary conditions. While the flexibility
to change initial/boundary conditions
is quite common, two-point numerical fluxes are also just functions with a
specified signature. Thus, users can implement numerical fluxes in their
own code and they will work and be as efficient as if they were implemented
directly in \trixi.
